Relevance Modeling with Documents Expanded Using External Collections

### 2017-02-14 paper.tex
only one model section to save space, and other small changes

\subsection{Basic Model}\label{section.model.basic}

We would now like to incorporate our expansion documents into a retrieval model over documents. We assume that a query is generated by a mixture of the original document language model $\theta_D$ and a language model $\theta_E$ representing the expansion documents. We assume that $\theta_E$ can be estimated using the text of the expansion documents $\mathcal{E}_D$. This mixture model may be expressed as:
%
\begin{flalign}\label{eq.ql-and-expansion}
	\hat{P}^\lambda(Q|D) &= \prod_{i=1}^{|Q|} (1-\lambda) P(q_i|D) + \lambda P(q_i|\mathcal{E}_D)
\end{flalign}

\noindent with $0 \leq \lambda \leq 1$. The larger $\lambda$ is, the more we believe that the expansion documents are a good representation of $Q$ and the less we believe that the original document represents the ``true'' language model of $Q$. We estimate $P(q_i|\mathcal{E}_D)$ in expectation:
%
\begin{flalign}\label{eq.expansion-sum}
	P(q_i|\mathcal{E}_D) &= \sum_{E \in \mathcal{E}_D} P(q_i|E) P(E|D) .
\end{flalign}

\noindent Like $P(q_i|D)$, we estimate the probability of $q_i$ given expansion document $E$, $P(q_i|E)$, as a Dirichlet-smoothed query likelihood. By virtue of our expansion document scoring and normalization, we also have $P(E|D)$.

\subsection{Combining Evidence}\label{section.combining}

We investigate the use of multiple collections for document expansion. We expect a more diverse set of expansion documents to result in more robust language models at the conclusion of the expansion process.

To expand a document $D$ given a set of collections $C = \{C_1, C_2, ..., C_n\}$, we first construct a set of expansion documents ${\mathcal{E}_D}_i$ using $C_i$ in the manner described in Section \ref{section.expanding}. We may incorporate these multiple sets of expansion documents by simply altering Eq. \ref{eq.ql-and-expansion} to sum over $\mathcal{E}_D$ terms:

\begin{flalign}\label{eq.ql-and-expansion-mult}
	\hat{P}^\lambda(Q|D) &= \prod_{i=1}^{|Q|} (1-\sum_{j=1}^n \lambda_{{\mathcal{E}_D}_j}) P(q_i|D) + \sum_{j=1}^n \lambda_{{\mathcal{E}_D}_j} P(q_i|{\mathcal{E}_D}_j)
\end{flalign}

\noindent where $0 \leq \sum_{j=1}^n \lambda_{{\mathcal{E}_D}_j} \leq 1$. As before, each value of $\lambda_{{\mathcal{E}_D}_j}$ reflects our confidence in that set of expansion documents accurately representing the query language model.

@@

Although Eq. \ref{eq.ql-and-expansion-mult} allows for an arbitrary number of collections, for now we limit ourselves to two: the collection that the document appears in (the ``target'' collection) and Wikipedia; the latter, as a general knowledge encyclopedia, is hypothesized to yield relatively unbiased probability estimates. We build an Indri\footnote{http://www.lemurproject.org/indri/} index over the Wikipedia page text.

@@

These datasets were chosen because they provide a good range of collection types, from relatively homogeneous with well-formed documents (AP) to heterogeneous with varied document quality (wt10g).

@@

Stop words are removed from the query and document pseudo-query for all runs. For efficiency, we retrieve the top 1000 documents per query using the default Indri query likelihood implementation and re-rank these documents based on their expanded representations as described in Section \ref{section.model}.

@@

For this work, we set $k$ heuristically. In principle, this parameter need not be limited beyond the length of the document; however, this would increase computation time significantly, so we have opted to set it to a reasonable value. The parameter $n$ is similarly set heuristically to 10 expansion documents; see Section \ref{section.n-sensitivity} for a discussion of the performance sensitivity to the setting of $n$.

The values of $\lambda_{\mathcal{E}_D}$ and $\alpha$, are determined using 10-fold cross-validation. In the training stage, we sweep over parameter values in intervals of 0.1. The results of each test fold for a given run are concatenated to form a complete set of topics.

>>>>

We would now like to incorporate our expansion documents into a retrieval model over documents. We assume that a query is generated by a mixture of the original document language model $\theta_D$ and language models ${\theta_E}_j$ representing the expansion documents each corpus $C_j \in \{C_1, C_2, ..., C_n\}$. We assume that ${\theta_E}_j$ can be estimated using the text of the expansion documents ${\mathcal{E}_D}_j$ in corpus $C_j$. This mixture model may be expressed as:
%
\begin{flalign}\label{eq.ql-and-expansion-mult}
	\hat{P}^\lambda(Q|D) &= \prod_{i=1}^{|Q|} (1-\sum_{j=1}^n \lambda_{{\mathcal{E}_D}_j}) P(q_i|D) + \sum_{j=1}^n \lambda_{{\mathcal{E}_D}_j} P(q_i|{\mathcal{E}_D}_j)
\end{flalign}
%\begin{flalign}\label{eq.ql-and-expansion}
%	\hat{P}^\lambda(Q|D) &= \prod_{i=1}^{|Q|} (1-\lambda) P(q_i|D) + \lambda P(q_i|\mathcal{E}_D)
%\end{flalign}

\noindent where $0 \leq \sum_{j=1}^n \lambda_{{\mathcal{E}_D}_j} \leq 1$. We estimate $P(q_i|{\mathcal{E}_D}_j)$ in expectation:
% %The larger $\lambda$ is, the more we believe that the expansion documents are a good representation of $Q$ and the less we believe that the original document represents the ``true'' language model of $Q$.
\begin{flalign}\label{eq.expansion-sum}
	P(q_i|{\mathcal{E}_D}_j) &= \sum_{E \in {\mathcal{E}_D}_j} P(q_i|E) P(E|D) .
\end{flalign}

\noindent Like $P(q_i|D)$, we estimate the probability of $q_i$ given expansion document $E$, $P(q_i|E)$, as a Dirichlet-smoothed query likelihood. By virtue of our expansion document scoring and normalization, we also have $P(E|D)$. This general model may be used with any number of expansion corpora.

@@

Although Eq. \ref{eq.ql-and-expansion-mult} allows for an arbitrary number of collections, for now we limit ourselves to two: the collection that the document appears in (the ``target'' collection) and Wikipedia\footnote{http://en.wikipedia.org}; the latter, as a general knowledge encyclopedia, is hypothesized to yield relatively unbiased probability estimates. We build an Indri\footnote{http://www.lemurproject.org/indri/} index over the Wikipedia page text.

@@

These datasets provide a good range of collection types, from relatively homogeneous with well-formed documents (AP) to heterogeneous with varied document quality (wt10g).

@@

Stop words are removed from the query. For efficiency, we retrieve the top 1000 documents per query using the default Indri query likelihood implementation and re-rank these documents based on their expanded representations as described in Section \ref{section.model}.

@@

For this work, we set $k$ heuristically. In principle, this parameter need not be limited beyond the length of the document; however, this would increase computation time significantly, so we have set it to a reasonable value. The parameter $n$ is also set heuristically; see Section \ref{section.n-sensitivity} for a discussion of the performance sensitivity to the setting of $n$.

The values of $\lambda_{\mathcal{E}_D}$ and $\alpha$, are determined using 10-fold cross-validation. In the training stage, we sweep over parameter values in intervals of 0.1. The concatenated results of each test fold form a complete set of topics.
